---
title: "benchmarkingResults"
output: html_document
date: "2023-06-26"
---

# load libraries
```{r}
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
```

# V1
make dataframes
all
```{r}
all_df <- as.data.frame(read.table("benchmarkingResults_all.csv", sep = ",", header = TRUE))
```
panel a (a constant, b increasing)
```{r}
a100_df <- all_df[all_df$a == 100, ]
a1k_df <- all_df[all_df$a == 1000,]
a100k_df <- all_df[all_df$a == 100000,]
a10mi_df <- all_df[all_df$a == 10000000,]
```
panel b (b constant, a increasing)
```{r}
b100_df <- all_df[all_df$b == 100, ]
b1k_df <- all_df[all_df$b == 1000, ]
b100k_df <- all_df[all_df$b == 100000,]
b10mi_df <- all_df[all_df$b == 10000000, ]
```
panel c (both a and b increasing)
```{r}
c_df <- all_df[all_df$a == all_df$b,]
```

make plots
panel a (a constant, b increasing)
```{r}
a100_plot <- ggplot(data=a100_df, aes(x=b, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file a size constant = 100, file b size increasing")

a1k_plot <- ggplot(data=a1k_df, aes(x=b, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file a size constant = 1k, file b size increasing")

a100k_plot <- ggplot(data=a100k_df, aes(x=b, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file a size constant = 100k, file b size increasing")

a10mi_plot <- ggplot(data=a10mi_df, aes(x=b, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file a size constant = 10mi, file b size increasing")
```
panel b (b constant, a increasing)
```{r}
b100_plot <- ggplot(data=b100_df, aes(x=a, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file b size constant = 100, file a size increasing")

b1k_plot <- ggplot(data=b1k_df, aes(x=a, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file b size constant = 1k, file a size increasing")

b100k_plot <- ggplot(data=b100k_df, aes(x=a, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file b size constant = 100k, file a size increasing")

b10mi_plot <- ggplot(data=b10mi_df, aes(x=a, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file b size constant = 10mi, file a size increasing")
```
panel c (both a and b increasing)
```{r}
c_plot <-
  ggplot(data=c_df, aes(x=a, y=ns.op, color=Tool)) +
  geom_line() +
  geom_point() +
  ggtitle("file a size = file b size")
```
put panels together
```{r}
figure <- ggarrange(a100_plot, a1k_plot, a100k_plot, a10mi_plot, 
                    b100_plot, b1k_plot, b100k_plot, b10mi_plot,
                    c_plot,
                    labels = c("A1", "A2", "A3", "A4", "B1","B2", "B3", "B4", "C"),
                    ncol = 4, nrow = 3)
```

# V2
from Riley's plotBenchMarks.r
```{r}
data <- read.csv("benchmarkingResults_all.csv", sep=",", header=TRUE)

myPal <- c("#577590", "#364959", "#90bd6d", "#FF0000") 

# when plotting, got some warnings, but not errors, so hopefully they are ok

a_plot <- ggscatter(subset(data, a == 1000), x="b", y="ns.op", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+yscale("log10", .format=TRUE)+xscale("log10", .format=TRUE)+ylab("Nanoseconds per Operation")+xlab("Input File Size")+ggtitle("a=1000, b increasing")

b_plot <- ggscatter(subset(data, b == 10000000), x="a", y="ns.op", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+yscale("log10", .format=TRUE)+xscale("log10", .format=TRUE)+ylab("Nanoseconds per Operation")+xlab("Select File Size")+ggtitle("b=10mi, a increasing")

# just doing subset(data, a == b) didn't work to create correct df, so I did make another df
c_df <- data[data$a == data$b,]
c_plot <- ggscatter(c_df, x="b", y="ns.op", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+yscale("log10", .format=TRUE)+xscale("log10", .format=TRUE)+ylab("Nanoseconds per Operation")+xlab("Input File Size")+ggtitle("a=b, a and b increasing")
```

# V3
threads optimization
```{r}
dataThreads <- read.csv("benchmarkingResultsThreads.csv", sep=",", header=TRUE)

threads_plot <- ggscatter(dataThreads, x="threads", y="ns.op", add="loess", conf.int=TRUE)+
  yscale("log10", .format=TRUE)+
  ylab("Nanoseconds per Operation")+
  xlab("number of threads")+
  ggtitle("a=10mi, b=10mi")
```

# V4
# Final Run
load data
```{r}
data <- read.csv("benchmarkingResults_all.csv", sep=",", header=TRUE)
```
speed
a_plot
```{r}
myPal <- c("#577590", "#364959", "#FF0000", "#CC99FF", "#90bd6d", "#FF8000") 

a_plot <- ggscatter(subset(data, a == 1000), x="b", y="ns.op", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+yscale("log10", .format=TRUE)+xscale("log10", .format=TRUE)+ylab("Nanoseconds per Operation")+xlab("Input File Size")+ggtitle("a=1000, b increasing")

# with subsetting Tool, only 4 tools (bedops, bedtools, gonomics1worker, gonomics4worker)
# subset(data, a == 1000, Tool %in% c('Bedops', 'Bedtools', 'Gonomics1Worker', 'Gonomics4Worker') ) didn't work, so I did make another df
a_df <- data[data$Tool %in% c('Bedops', 'Bedtools', 'Gonomics1Worker', 'Gonomics4Worker'), ]
  
myPal <- c("#577590", "#364959", "#92DC59", "#90bd6d") 

a_plot <- ggscatter(subset(a_df, a == 1000), x="b", y="ns.op", color= "Tool", add="loess", conf.int=TRUE, palette=myPal)+yscale("log10", .format=TRUE)+xscale("log10", .format=TRUE)+ylab("Runtime (ns/op)")+xlab("Input File Size (number of entries)")+ggtitle("Select File Size = 1,000 entries")
```
b_plot
```{r}
# made another df to make coloring appear better, otherwise ggplot will plot 4-color and then 6-color because it's confused that not all 6 Tools show up in the b=10mi subset
b_df <- data[data$Tool %in% c('Bedops', 'Bedtools', 'Gonomics1Worker', 'Gonomics8Worker'), ]

myPal <- c("#577590", "#364959", "#92DC59", "#90bd6d") 

b_plot <- ggscatter(subset(b_df, b == 10000000), x="a", y="ns.op", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+yscale("log10", .format=TRUE)+xscale("log10", .format=TRUE)+ylab("Runtime (ns/op)")+xlab("Select File Size (number of entries)")+ggtitle("Input File Size = 10,000,000 entries")
```
c_plot
```{r}
# just doing subset(data, a == b) didn't work to create correct df, so I did make another df
c_df <- data[data$a == data$b,]

myPal <- c("#577590", "#364959", "#FF0000", "#CC99FF", "#90bd6d", "#FF8000") 

c_plot <- ggscatter(c_df, x="b", y="ns.op", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+yscale("log10", .format=TRUE)+xscale("log10", .format=TRUE)+ylab("Nanoseconds per Operation")+xlab("Input File Size")+ggtitle("a=b, a and b increasing")
```
memory
a_plot
```{r}
myPal <- c("#577590", "#364959", "#FF0000", "#CC99FF", "#90bd6d", "#FF8000") 

a_plot <- ggscatter(subset(data, a == 1000), x="b", y="memUsage", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+xscale("log10", .format=TRUE)+ylab("Memory Usage")+xlab("Input File Size")+ggtitle("a=1000, b increasing")
```
b_plot
```{r}
myPal <- c("#577590", "#364959", "#FF0000", "#CC99FF", "#90bd6d", "#FF8000") 

b_plot <- ggscatter(subset(data, b == 10000000), x="a", y="memUsage", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+xscale("log10", .format=TRUE)+ylab("Memory Usage")+xlab("Select File Size")+ggtitle("b=10mi, a increasing")
```
c_plot
```{r}
# just doing subset(data, a == b) didn't work to create correct df, so I did make another df
c_df <- data[data$a == data$b,]

myPal <- c("#577590", "#364959", "#FF0000", "#CC99FF", "#90bd6d", "#FF8000") 

c_plot <- ggscatter(c_df, x="b", y="memUsage", color="Tool", add="loess", conf.int=TRUE, palette=myPal)+xscale("log10", .format=TRUE)+ylab("Memory Usage")+xlab("Input File Size")+ggtitle("a=b, a and b increasing")
```